The instability of variational quantum mechanics with Gaussian approximants is (not) entirely due to the unstable least squares problem

### 2013-06-11 paper.tex
task

>>>>

To do this, we need some bracket matrices.  The representation used is
$$|ψ(φ,α)〉=e^{φ+αa†}|0〉=e^{φ+½|α|²}|α〉,$$
whence
$$|Dψ(φ,α)〉=(1,a†)|ψ(φ,α)〉.$$
The bracket with the number states is easily evaluated:
$$〈n|Dψ(φ,α)〉=e^φ\pmatrix{{α^n\over \sqrt{n!}} &  α^{n-1}\sqrt{n\over (n-1)!}},$$
as is the bracket of the quartic oscillator Hamiltonian $a^{2\dagger}a²$
$$〈n|H|ψ(φ,α)〉=e^φα^n\sqrt{n(n-1)\over(n-2)!}.$$
